---
output: github_document
---

```{r packages, include = FALSE}
library("httr")
library("jsonlite")
library("financeR")
library("ggplot2")
library("lubridate")
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# financeR

<!-- badges: start -->
<!-- badges: end -->


## Pull big amounts of stock and financial data from the 'financialmodelingprep' API
A wrapper for pulling stock and financial data from the 'financialmodelingprep' API <https://financialmodelingprep.com/developer/docs/> in bulk.

## Installation

You can install the released version of financeR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("financeR")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("oliealex/Stock-analysis")
```

Required packages are: 
``` r
require(httr) 
require(jsonlite)
```

## Authentication

First, set up an account with <https://financialmodelingprep.com/> and retrieve your api key, then make sure to set your api key as follwing.

```{r authentication}
api <- 'xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx'

```


## Example

Do you want to see historical stock data?:

```{r example}
library(financeR)
api <- "42632c388365783ab0c341411f47ae80"

PLTR <- historic_price(ticker = "PLTR", time = "full", api_key = api)
head(PLTR)
```

Or maybe plot the historical stock prices?:

```{r indicators}
library(financeR)
library(lubridate)
library(ggplot2)
api <- "42632c388365783ab0c341411f47ae80"

AAPL <- historic_price(ticker = "AAPL", time = "full", api_key = api)
AAPL$date <- as.Date(AAPL$date)
plot <- ggplot(AAPL, aes(x = date, y = close)) +
  geom_line(colour = "red") +
  theme_bw()
plot



```
